### 2024-08-11 machine-learning.qmd
20240811 - drop variables from second step

```{r}
# Create lists of objects to merge, depending on data structure: id; or id-season; or id-season-week
#-todo: remove redundant variables
playerListToMerge <- list(
  nfl_players %>% filter(!is.na(gsis_id)) %>% select(-season, -years_of_experience),
  nfl_draftPicks %>% filter(!is.na(gsis_id)) %>% select(-season, -age)
)

@@

seasonalData <- powerjoin::power_full_join(
  playerSeasonMerged,
  playerMerged %>% select(-team, -team_abbr, -team_seq, -current_team_id),
  by = "gsis_id",
  conflict = coalesce_xy
) %>% 
  filter(!is.na(season)) %>% 
  select(gsis_id, season, player_display_name, position, team, games, everything())

>>>>

```{r}
# Create lists of objects to merge, depending on data structure: id; or id-season; or id-season-week
#-todo: remove redundant variables
playerListToMerge <- list(
  nfl_players %>% filter(!is.na(gsis_id)) %>% select(-season),
  nfl_draftPicks %>% filter(!is.na(gsis_id)) %>% select(-season)
)

@@

seasonalData <- powerjoin::power_full_join(
  playerSeasonMerged,
  playerMerged %>% select(-age, -years_of_experience, -team, -team_abbr, -team_seq, -current_team_id),
  by = "gsis_id",
  conflict = coalesce_xy
) %>% 
  filter(!is.na(season)) %>% 
  select(gsis_id, season, player_display_name, position, team, games, everything())
